---
title: "gasoline mileage"
output: html_notebook
---

```{r setup}
library(readxl)
Book3 <- read_excel("Book3.xlsx", range = "a13:b23")

valA = c(Book3$`Program A`)
valB = c(Book3$`Program B`)
```

## assumption
H0: variance of A and B is equal.  
H1: not H0.  
significant level: 5%  

## 1. Check if equal variances or not (F test)
```{r}
var.test(valA, valB)
```
F test shows variance of A and B is equal.  
P value (0.3818) is greater than 5%.  H0 is not rejected.

## 2. If equal variance, use 2 samples T test with equal variances
### assumption
H0: mean of A and B is equal.  
H1: not H0  
significant level: 5%  
Variance of A and B is equal.  

```{r}
t.test(valA, valB, var.equal = T)
```
T test shows mean of A and B is not equal.  
P value (0.00526) is less than 5%.  H0 is rejected.  

### assumption
H0: mean of A and B is equal.  
H1: mileage of A is better than B -> mean of A is greater than B.  
significant level: 5%  
Variance of A and B is equal.  

```{r}
t.test(valA, valB, var.equal = T, alternative = "greater")
```
T test shows mean of A and B is not equal.  
P value (0.00263) is less than 5%.  H0 is rejected.  

### assumption
H0: mean of A and B is equal.  
H1: mileage of B is better than A -> mean of A is smaller than B.  
significant level: 5%  
Variance of A and B is equal.  

```{r}
t.test(valA, valB, var.equal = T, alternative = "less")
```
T test shows mean of A and B is not equal.  
P value (0.9974) is greater than 5%.  H0 is not rejected.  

## conclusion
Program A has positive impact to Program B.